Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-17 paper/main.tex
Simplify

% intro
We tested our modeled hemodynamic responses based on stimulus annotations by
conducting standard two-level GLM analyses to create
participant-specific results across the 8 segments for every participant and each
stimulus.
% level 3
Subsequent, third-level analyses averaged contrast estimates over participants.

>>>>

% intro
We performed standard two-level GLM analyses to aggregate results across the 8
segments for every participant and each stimulus separately.
% level 3
Subsequently, we conducted third-level analyses to average contrast estimates
over participants for each stimulus, respectively.
